Tweets

### 2020-05-15 Rmd/tweets.Rmd
updated tweets stop list

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
```

>>>>

```{r}
# create a twitter-specific stop word list
twitter_stop <- tibble::tibble(word = c("https", "http", "t.co", "amp"))
# get a list of english language words and names
library(qdapDictionaries) # contains object GradyAugmented
```
